---
page-layout: full
from: markdown+emoji
---

# Processing data

The file [1_process.R](1_process.R) contains the 
code for processing the data, which involved the following steps:   

1) Importing all data files (wide format) and merging them into one dataset (long format);  
2) Correcting spelling for names with special characters across all countries;  
3) Including expected values for sex, region, country, religion for each name (from dictionary);  
4) Exporting the data to R, SPSS, and STATA formats. 

## Final dataset

The code below reads the exported dataset in RDS format. The SPSS `.sav` and STATA `.dat` files are also available on the data subdirectory. 

```{r}
# Import packages and working dataset
library(tidyverse)
library(haven)
library(plotly)
library(gt)

df_es <- readRDS("./data/ES2_NameSurvey_2025-01-24.RDS")

```

@tbl-totals shows the total number of observations (tests) for each country as well as the number of names tested.  


```{r}
#| tbl-cap: Total number of distinct names tested and tests by country
#| label: tbl-totals

df_es |> 
    group_by(country_survey) |>
    summarise(Names = n_distinct(Name),
              Tests = n()) |>
    gt()
```
